ManuscriptPURFits

### 2024-02-07 Code/ManuscriptPURFits.Rmd
Edit code

remove(DummyDF_Expand)

@@

```{r testplot}
 PURPARFits %>% 
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
    scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
  facet_grid(rows = vars(Par_ue), cols = vars(Strain)) +
  theme_bw()
```

@@

#constrain with lower 0 and upper 1 limits to avoid excessive Pmax and negative b

# PURPARStrainO2Nest <- PURPARFits |>
#   nest(data = -c("Strain","O2_uM")) |>
#   mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PUR_day, a, Pmax),
#                               data = .x,
#                               start = list(a = 1e-6,
#                                            Pmax = 1),
#                               lower = c(0, 0),
#                               upper = c(1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRC_Param = map(GRC_Model, tidy),
#          GRC_Predict = map(GRC_Model, possibly(augment), NULL),
#          GRC_Glance = map(GRC_Model, possibly(glance))) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )

@@

PURPARStrainO2PhotoNestModels_filtered <- PURPARFits_dummy |>
   filter(PURPhotonDose_day <= 1.5e+06) |>
 nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
                              lower = c(-0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

@@

# Plot fits
```{r growthPURplots, fig.height= 10, fig.width= 10}
#ReplicateMean_

# PURPARStrainWLNest |>
#   #filter(!is.null(GRC_Model)) |>
#   filter(!map_lgl(GRC_Model, is.null)) |>  
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(WL), cols = vars(Strain)) + 
#   theme_bw()

# PURPARStrainO2Nest |>
#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#     labs(title = "PURPARStrainO2Nest GRC") +
#   theme_bw()

# PURPARStrainO2NestModels |>
#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#     labs(title = "PURPARStrainO2NestModels GRC") +
#   theme_bw()

# PURPARStrainO2Nest |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#     labs(title = "PURPARStrainO2Nest Platt") +
#   theme_bw()
#

# PURPARStrainO2NestModels |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |> # only include fits that did not fail
#   unnest(GRCplatt_Predict, data) |>
#    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
#          Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#   labs(title = "PURPARStrainO2NestModels Platt") +
#   theme_bw()

PURPARStrainO2NestModels_filtered|>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
  labs(title = "PURPARStrainO2NestModels_filtered Platt") +
  theme_bw()

# PURPARStrainO2PhotoNestModels |>
#   filter(!map_lgl(GRC_Model, is.null)) |>
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoNestModels GRC") +
#   theme_bw()

# PURPARStrainO2PhotoNestModels |>
#    filter(!map_lgl(GRC_Model, is.null)) |>
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoNestModels GRC") +
#   theme_bw()

# PURPARStrainO2PhotoNestModels |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoNestModels Platt") +
#   theme_bw()

PURPARStrainO2PhotoNestModels_filtered |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +   
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoNestModels_filtered Platt") +
  theme_bw()

PURPARStrainO2PhotoNestModels_filtered |>
  filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(GRClm_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
   scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoNestModels_filtered Linear Model") +
  theme_bw()

@@

# PURPARStrainO2WLNestModels |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
#          Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2WLNestModels Platt") +
#   theme_bw()

# PURPARStrainO2PeriodWLNest |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod, WL), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PeriodWLNest Platt") +
#   theme_bw()

@@

nlsLM generates AIC accessed with broom::glance
Choose best model between platt and lm based on lowest GIC 
```{r aic comparisons}
#https://www.scribbr.com/statistics/akaike-information-criterion/

#need to remove 'null' models to facilitate conversion of AIC from 'list' derived from 'Glance' column, to dbl
# PURPARStrainO2BestModels <- PURPARStrainO2Nest|>
#   select(-c(data)) |>
#   pivot_longer(cols = -c(Strain, O2_uM)) |>
#   drop_na(value) |>
#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
#   pivot_wider(names_from = Output, values_from = value) |>
#   filter(!map_lgl(Model, is.null)) |>
#   filter(!map_lgl(Glance, is.null)) |>
#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
#   group_by(Strain, O2_uM) |>
#   filter(AIC == min(AIC)) |>
#   ungroup() |>
#   select(-c(Model, Glance)) |>
#   unnest(Param) |>
#   select(-c(statistic)) |>
#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
#  
# PURPARStrainO2BestModels

# PURPARStrainO2BestModels <- PURPARStrainO2NestModels|>
#   # select(-c(data)) |>
#   pivot_longer(cols = -c(Strain, O2_uM, data)) |>
#   drop_na(value) |>
#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
#   pivot_wider(names_from = Output, values_from = value) |>
#   filter(!map_lgl(Model, is.null)) |>
#   filter(!map_lgl(Glance, is.null)) |>
#   mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
#   group_by(Strain, O2_uM) |>
#   filter(AIC == min(AIC)) |>
#   ungroup() |>
#   select(-c(Model, Glance)) |>
#   unnest(Param) |>
#   select(-c(statistic)) |>
#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
#  
# PURPARStrainO2BestModels

# PURPARStrainO2BestModels_filtered <- PURPARStrainO2NestModels_filtered|>
#   # select(-c(data)) |>
#   pivot_longer(cols = -c(Strain, O2_uM, data)) |>
#   drop_na(value) |>
#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
#   pivot_wider(names_from = Output, values_from = value) |>
#     filter(!map_lgl(Model, is.null)) |>
#   filter(!map_lgl(Glance, is.null)) |>
#   mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
#   group_by(Strain, O2_uM) |>
#   filter(AIC == min(AIC)) |>
#   ungroup() |>
#   select(-c(Model, Glance)) |>
#   unnest(Param) |>
#   select(-c(statistic)) |>
#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
#  
# PURPARStrainO2BestModels_filtered
# 
# PURPARStrainO2PhotoBestModels_filtered <- PURPARStrainO2PhotoNestModels_filtered|>
#   # select(-c(data)) |>
#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
#   drop_na(value) |>
#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
#   pivot_wider(names_from = Output, values_from = value) |>
#   filter(!map_lgl(Model, is.null)) |>
#   filter(!map_lgl(Glance, is.null)) |>
#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
#   group_by(Strain, O2_uM, Photoperiod) |>
#   filter(AIC == min(AIC)) |>
#   ungroup() |>
#   select(-c(Model, Glance)) |>
#   unnest(Param) |>
#   select(-c(statistic)) |>
#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
# 
# PURPARStrainO2PhotoBestModels_filtered

# PURPARStrainO2PhotoBestModels <- PURPARStrainO2PhotoNestModels|>
#   # select(-c(data)) |>
#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
#   drop_na(value) |>
#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
#   pivot_wider(names_from = Output, values_from = value) |>
#   filter(!map_lgl(Model, is.null)) |>
#   filter(!map_lgl(Glance, is.null)) |>
#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
#   group_by(Strain, O2_uM, Photoperiod) |>
#   filter(AIC == min(AIC)) |>
#   ungroup() |>
#   select(-c(Model, Glance)) |>
#   unnest(Param) |>
#   select(-c(statistic)) |>
#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
#  
# PURPARStrainO2PhotoBestModels

# PURPARStrainO2WLBestModels <- PURPARStrainO2WLNestModels|>
#   # select(-c(data)) |>
#   pivot_longer(cols = -c(Strain, O2_uM, WL, data)) |>
#   drop_na(value) |>
#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
#   pivot_wider(names_from = Output, values_from = value) |>
#  filter(!map_lgl(Model, is.null)) |>
#   filter(!map_lgl(Glance, is.null)) |>
#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
#   group_by(Strain, O2_uM, WL) |>
#   filter(AIC == min(AIC)) |>
#   ungroup() |>
#   select(-c(Model, Glance)) |>
#   unnest(Param) |>
#   select(-c(statistic)) |>
#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
#  
# PURPARStrainO2WLBestModels

# PURPARStrainO2PhotoWLBestModels <- PURPARStrainO2PhotoNestModels|>
#   select(-c(data)) |>
#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, WL)) |>
#   drop_na(value) |>
#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
#   pivot_wider(names_from = Output, values_from = value) |>
#   filter(!map_lgl(Model, is.null)) |>
#   filter(!map_lgl(Param, is.null)) |>
#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
#   group_by(Strain, O2_uM, Photoperiod) |>
#   filter(AIC == min(AIC)) |>
#   ungroup() |>
#   select(-c(Model, Glance)) |>
#   unnest(Param) |>
#   select(-c(statistic)) |>
#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
#  
# PURPARStrainO2PhotoWLBestModels

# mutate(Pmax_Ye = if_else(ModelType == "GRCbeta", estimate_a * ((sqrt(estimate_b + estimate_g) - sqrt(estimate_b))/estimate_g)^2, NA))

#filter to keep platt models
KeepPlattModel <- PURPARStrainO2PhotoNestModels_filtered|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
KeepLmModel <- PURPARStrainO2PhotoNestModels_filtered|>
  filter(map_lgl(GRCplatt_Model, is.null)) |>
 select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))

@@

 StrainO2Photofiltered_PlattLmModel <- StrainO2Photoperiod_AllModels |>
   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, Photoperiod) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

 #filter to keep platt models
KeepPlattModel <- PURPARStrainO2NestModels_filtered|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

@@

 StrainO2filtered_PlattLmModel <- StrainO2_AllModels|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Glance))|>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

 remove(KeepPlattModel)
 remove(KeepLmModel)
 # remove(PURPARStrainO2NestModels_filtered)
 # remove(PURPARStrainO2PhotoNestModels_filtered)

@@

StrainO2filtered_PlattLmModel <- StrainO2filtered_PlattLmModel|>
  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))

@@

# PURPARStrainO2WLBestModels <- PURPARStrainO2WLBestModels|>
#   mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
#          estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
#          estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
#          AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC)) 
#  
# PURPARStrainO2WLBestModels

StrainO2Photofiltered_PlattLmModel <- StrainO2Photofiltered_PlattLmModel|>
  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))

StrainO2Photofiltered_PlattLmModel

@@

```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}

# make wider to join with DF that contains the 1 fit through all photoperiods
Wider_Photoperiods <- StrainO2Photofiltered_PlattLmModel %>% 
  select(Strain, Photoperiod, O2_uM, Model) %>% 
  pivot_wider(names_from = Photoperiod, values_from = Model)

# this contains 1 fit through all photoperiods, the photoperiods with no growth were filtered out.
AllPhotoperiods <- StrainO2filtered_PlattLmModel %>% 
  select(Strain, O2_uM, Model) %>% 
 rename(All = 'Model')

CombinePhotoperiods <- left_join(Wider_Photoperiods, AllPhotoperiods)

>>>>

remove(DummyDF_Expand)
remove(PURPARFits)

@@

```{r testplot}
 PURPARFits_dummy %>% 
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
    scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
  facet_grid(rows = vars(Par_ue), cols = vars(Strain)) +
  theme_bw()
```

@@

@@

PURPARStrainO2PhotoNestModels <- PURPARFits_dummy |>
   filter(PURPhotonDose_day <= 1.5e+06) |>
 nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
                              lower = c(-0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

@@

# Plot fits
```{r growthPURplots, fig.height= 10, fig.width= 10}

# PURPARStrainO2NestModels |>
#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
PURPARStrainO2NestModels_filtered|>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
  labs(title = "PURPARStrainO2NestModels_filtered Platt") +
  theme_bw()

PURPARStrainO2PhotoNestModels |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +   
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoNestModels Platt") +
  theme_bw()

PURPARStrainO2PhotoNestModels |>
  filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(GRClm_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
   scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoNestModels Linear Model") +
  theme_bw()

@@

@@

# Want platt model for all fits that did not fail and lm for platt models that returned a NULL
```{r}
# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
#filter to keep platt models
KeepPlattModel <- PURPARStrainO2PhotoNestModels|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
KeepLmModel <- PURPARStrainO2PhotoNestModels|>
  filter(map_lgl(GRCplatt_Model, is.null)) |>
 select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))

@@

# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
 StrainO2Photoperiod_PlattLmModel <- StrainO2Photoperiod_AllModels |>
   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, Photoperiod) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

# O2 nested data frame containing the single fit of pooled photoperiods 
 #filter to keep platt models
KeepPlattModel <- PURPARStrainO2NestModels_filtered|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

@@

# O2 nested data frame containing the single fit of pooled photoperiods 
 StrainO2filtered_PlattLmModel <- StrainO2_AllModels|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Glance))|>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

 remove(KeepPlattModel)
 remove(KeepLmModel)
 remove(StrainO2Photoperiod_AllModels)
 remove(StrainO2_AllModels)

@@

# O2 nested data frame containing the single fit of pooled photoperiods for each strain 
StrainO2filtered_PlattLmModel <- StrainO2filtered_PlattLmModel|>
  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))

@@

# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
StrainO2Photoperiod_PlattLmModel <- StrainO2Photoperiod_PlattLmModel|>
  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))

StrainO2Photoperiod_PlattLmModel

@@

# ANOVA comparison of single fit through pooled photoperiods for each strain and [O2] to the fit of each photoperiod in that pool. 
```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}

# make wider to join with DF that contains the 1 fit through all photoperiods
Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
  select(Strain, Photoperiod, O2_uM, Model, Predict) %>% 
  pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict))

# this contains 1 fit through all photoperiods, the photoperiods with no growth were filtered out.
AllPhotoperiods <- StrainO2filtered_PlattLmModel %>% 
  select(Strain, O2_uM, Model, Predict, data) %>% 
 rename(All = 'Model',
        Predict_all = 'Predict',
        Data_all = 'data')
